### 2022-11-18 manuscript.rmd
add r1

---
title             : "Bayesian (comparative) journalism studies"
shorttitle        : "BAYESIAN MULTILEVEL REGRESSION"

@@

abstract: |
  Comparative approaches such as comparative content analysis are frequently used in journalism studies. The purpose of this paper is to argue that researchers should refrain from using current (frequentist) analytical approaches to analyze data from a comparative study. It is because current approaches cannot account for non-atomicity (nested nature) and non-stochasticity (non-random sampling) of the data. Bayesian multilevel regression is suggested to be a ---and probably, the only--- valid analytical approach. Using the openly available *useNews* and *Worlds of Journalism Study* datasets and the R package *brms*, we demonstrate how to apply the Bayesian approach for the analysis of comparative data. We also address common queries of the approach such as choosing the priors and diagnosing the convergence of the model. Furthermore, we argue that choosing a Bayesian approach also solves the problem of often misinterpreted frequentist confidence intervals.

keywords          : "Bayesian inference, multilevel model, comparative communication research, ecological effect"
wordcount         : "8964"

@@

@@

Communication research is often comparative, journalism studies are increasingly so [@hanusch:2019:C]. Comparative approach is used in modeling journalistic culture [e.g. @esser:2013:C], comparative news value research [e.g. @burggraaff:2017:T;@wilke:2012], news flow research [e.g. @wu:2000:SDI;@grasland:2019:I], among others. Around 40% of recent  comparative studies in journalism research are comparative content analysis [@hanusch:2019:C], which include news articles from various outlets and usually also from various countries. Then the included news articles are coded either manually or automatically. Another 10% of recent comparative studies in journalism research are surveys such as the Worlds of Journalism Study (WJS) [@hanusch:2017:CJC].

Although some comparative studies are purely descriptive, most of these studies are aimed to study how contextual conditions such as characteristics of media outlets (e.g. political orientation, online versus offline) or their countries (e.g. post-communist country) influence the content of news articles or behaviors of journalists. For example, some hypotheses are "the coverage of foreign countries by the news is primarily determined by geographical proximity and the status of the covered country" [@wilke:2012, p.306] and "the  degree of opinion-orientation will be highest in newspapers from Polarized Mediterranean systems and lowest in those from Anglo-American systems." [@esser:2013:C] Employing the language from epidemiology [@susser:1994], the effect on media content and journalistic behaviors in these hypotheses is assumed to be ecological. It assumes a macro contextual factor (e.g., newspapers from Polarized Mediterranean systems) is associated with an outcome at the micro-level (e.g., degree of opinion-orientation), namely, the article-level or journalist-level.

This study of ecological effects on individual behaviors has a long tradition in social sciences. A famous example was Émile Durkheim's investigation on the ecological factors associated with suicide [@durkheim1897suicide]. Durkheim found a higher suicide rate among citizens from Scandinavian countries than those from other European countries. Using today’s standard, Durkheim's analysis is descriptive and this descriptive approach for studying ecological effect is indeed still useful for hypothesis generation in comparative research. An example of hypothesis-generating comparative research is <!-- redacted for ijoc  -->AUTHOR1 <!-- @chan2020combining -->, in which the sentiment profiles of terrorism coverage from Muslim- and Christian-majority countries were visualized. Hypothesis-generating comparative study, however, is rare. Most studies have a confirmatory outlook. As we see from the example hypotheses above, most of these studies propose hypotheses to test for ecological effects. In this context usually traditional (frequentist) hypothesis testing approaches were used: @esser:2013:C lumped multiple outlets from the same country together and then used univariate analysis of variance to test for the differences in the proportion of opinion-orienting articles across countries. In @wu:2000:SDI, multiple stepwise regression was used. These approaches violate the underlying assumptions of the statistical analyses. It highlights the fact that comparative research introduces a feature that researchers usually overlook: media contents are clustered in a multilevel structure. A news article is nested within its media outlet and its media outlet is in turn nested within its country. Such data structure brings two problems: non-atomicity and non-stochasticity.

In our paper, we first discuss these two issues before we suggest Bayesian multilevel regression as a standard approach for comparative research in journalism studies. While Bayesian models might be slightly more complicated to estimate in contrast to frequentist models as priors have to be chosen, these models allow researchers to make "principled statements about precision and plausibility" [@morey:2015 p. 121] and solve the issue of misinterpreted confidence intervals [@hoekstra:2014:R;@rinke:2018:PMA]. Using the openly available *useNews* and WJS datasets and the R package *brms*, we then demonstrate how to apply a Bayesian approach for the analysis of comparative data.

## Non-atomicity

*"When it comes to regression, multilevel regression deserves to be the default approach"* @mcelreath2020statistical [p. 356]

It is perhaps well-known what ecological fallacy is. We commit ecological fallacy, when we make inference at the micro-level (e.g. Eating more chocolate makes one cleverer) based on macro-level data (e.g. the correlation between countries' chocolate consumption and countries' number of Nobel winners). The reverse of ecological fallacy, i.e. making inference at macro-level based on micro-level data, is equally fallacious. This fallacy is called atomistic fallacy [@gnaldi:2018:EFC].

In comparative research, it is easy to incorrectly assume that macro-level independent variables (e.g. Anglo-American systems) could be analyzed at the same level as the micro-level dependent variable (e.g. the degree of opinion-orientation). The manifestation of this incorrect assumption is to enter macro-level variables as independent variables in multiple regression analysis and regress them against a micro-level dependent variable. Suppose one wants to study a classic news value question of how the probability of covering China changes when the hosting country of the media outlet has a higher trade volume with China. It is related to the news value of "meaningfulness" in @galtung:1965:SFN. The relationship can be expressed in the following regression equation: let $y_{i}$ be the dependent variable at the micro-level (coverage of China or not) and $x_{i}$ be the independent variable at the macro-level (trade volume with China). Suppose there are $m$ news articles where $i = 1,2,\ldots,m$.

@@

This method is the so-called "disaggregation approach". From an epistemic standpoint, searching for ecological effect by studying the value of slope ($\beta_{1}$) leads to atomistic fallacy [@hox2017multilevel]. From a statistical standpoint, this approach violates the underlying independence assumption. Almost all frequentist statistical tests assume that the observations are independent of each other: $y_{i}$ given $x_{i}$ are independently identically distributed (i.i.d.). Articles from the same media outlet are hardly i.i.d.: they are subjected to being edited by the same editorial team, to being written by the same group of journalists exposed to the same journalistic culture and paid for by the same employer. Also, the way communication researchers collect their media content resembles cluster sampling rather than random sampling: one usually starts from a specific media outlet and then collects all relevant articles from it. The choice of media outlets or countries is almost always not randomly selected. <!-- [^1] --> This sampling approach makes the independence assumption even more fragile.

@@

Previous simulation studies have shown that ignoring this dependence can lead to false-positive associations [e.g. @clarke:2008:W;@chen:2012:IIL]. The problem is more severe when the dependent variable is a discrete binary variable [@clarke:2008:W], a common feature of content analysis. <!-- [^2] -->

@@

There are two solutions to this. The first solution is to aggregate the micro-level dependent variable across a macro-level independent variable. Suppose there are $n$ countries in the above example. One can aggregate the total number of articles covering China as $z_{k}$ for the $k$-th country, where $k=i,\ldots,n$. Then, we can do a count-based regression with a regression equation like so:

\begin{equation}
  \label{eq:2}
  \log{z_{k}} = \beta_{0} + \beta_{1} x_{k} + \epsilon_{k}
\end{equation}

Using this aggregation method, the unit of analysis effectively switches from article to country. This method is useful when $x$ is the only independent variable, akin @esser:2013:C. It is not technically committing the atomistic fallacy, when one uses the value of slope as the evidence for an ecological effect. However, this method still has important drawbacks. First, it cannot be used for data with more than two levels. In @esser:2013:C, for example, multiple media outlets from the same country were lumped together and in effect, assumed to be homogeneous and the information about media outlets was discarded. Second, this method discards a massive amount of information. It is better for analysis of a dependent micro-level variable with a reasonable aggregation function (e.g. counting a binary variable). For numerical variables, aggregation functions such as taking a mean or median cannot capture the spread of the micro-level variable [@bryk:1988:H]. Also, the effective sample size is reduced from the number of articles ($m$) to the number of countries ($n$). Nonetheless, this aggregation method, although inflexible, is still useful when the number of groups (e.g. $n$) is large. It is also useful to collapse micro-levels (e.g. article-level) that are not useful in answering one’s research questions.

Another solution is to use the multilevel model (linear mixed model, or hierarchical model). In a multilevel model, the effect on the micro-level dependent variable ($y$) is modeled with equations at different levels. Using the above example, $y_{ik}$ denotes whether the $i$-th article in the $j$-th country is covering China; $x_{k}$ denotes the trade volume with China of the $k$-th country where the media outlet of $i$-th article is located.

@@

The benefit of using multilevel modeling lies in its flexibility in handling multi-level data. Suppose we also want to consider the clustering of articles around $o$ different media outlets in the above example and $j$-th media outlet is the media outlet of the $i$-th article, where $j = 1,\ldots, o$. The multilevel regression equations are rewritten as:

@@

@@

Multilevel modeling is the way to go for analyzing non-atomic data from comparative research. However, the conventional approach for statistical inference makes it not optimal. The conventional approach for statistical inference in multilevel modeling is maximum likelihood estimation (MLE). @stegmueller:2013:HMC demonstrates that MLE is associated with shrinkage (reduction of standard error, i.e. more false positives) and the shrinkage is more severe when the number of macro-level units (e.g. countries) is small. @stegmueller:2013:HMC proposes to use Bayesian analysis as a robust alternative [see counterarguments from @elff:2020:MAF;@bryan:2015:MMC]. Although less restrictive methods such as restricted maximum likelihood (REML) have been demonstrated to remediate the shrinkage issue of MLE [@elff:2020:MAF], we still agree with Stegmueller’s proposal for theoretical reasons. Our argument is more in line with @western:1994:BIC.

## Non-stochasticity

@@

Before diving into our theoretical reasoning, it is important to revisit what frequentist inference, the current default but often misunderstood [@rinke:2018:PMA] mode of inference in communication science, is. Under the frequentist framework, each experiment is assumed to be one of infinite independent, **repeatable** experiments on randomly drawn samples from a population. Random experiments are assumed to be repeated arbitrarily often. Based on this assumption and with just one experiment from the current study, we make an estimation about the population. The discrepancy between the estimation from that one experiment and the actual value of the population is due to sampling error alone, i.e. which subjects were randomly sampled from the population. Randomized surveys, for example, are assumed to be repeatable through repeated random sampling of the population. Suppose we replicated the same survey for 100 times and we would obtain a slightly different sample every time. We then calculated the 90\% confidence interval of the mean for each of these 100 surveys. We should anticipate that more or less 90 out of these 100 confidence intervals would include the true mean of the population. We cannot say for sure exactly 90 out of these 100 confidence intervals would include the true mean of the population because repeated random sampling is indeed random and the process is **stochastic**. However, we can say 90 is more probable than 0 or 100.

Comparative content analytic studies in journalism studies, unlike randomized surveys or randomized media experiments, often collect all available data. In contrast to sampling, these studies are actually doing a census of all data. There is no way to get more data unless the scope of these studies is changed [@berk:1995:SIA]. It is especially true for modern large-N studies using automated content analytic techniques. @burggraaff:2017:T, for instance, "collected all available news items from a selection of major Dutch news outlets, both online and print" (p. 6) and that amounted to 762,095 articles from 9 outlets in the period of 2014--2015.

Census-style studies are not repeatable and thus they generate non-stochastic data. In other words, data from comparative journalism studies are fundamentally irrelevant for frequentist inference [@western:1994:BIC]. P-values and confidence intervals generated do not have the same meaning as those from repeatable studies. According to @western:1994:BIC [p. 413], these values from non-stochastic data "lack meaning even as abstract propositions".

A common counterargument to this is the classic one from @deming:1941:ICS [p. 45], who suggested that "[a]s a basis for scientific generalizations and decisions for action, a census is only a sample." This notion assumes a census of a population can be used to make inference on a theoretical device called *superpopulation* which "theoretically could exist, may have existed, or may exist in the future" [@gibbs:2015:IU, p.3]. In other words, a finite census-as-a-sample census is assumed to be a “representative sample” of an infinite superpopulation. This counterargument could be useful but unlike a regular sample, whose representativeness can be assessed, we can never assess the representativeness of the census with respect to the theoretical superpopulation. Echoing the quote at the beginning of this paragraph, there is no way to tell if the current Czech history is representative of all possible Czech histories in the multiple parallel universes.

Instead of invoking the theoretical device of superpopulation, we follow the arguments from @western:1994:BIC and @stegmueller:2013:HMC for comparative studies: Bayesian inference should be used for analyzing data from comparative research in our field. Choosing a Bayesian approach also solves the problem of misinterpretation of confidence intervals [@hoekstra:2014:R;@rinke:2018:PMA]. Switching to a Bayesian approach addresses this issue as Bayesian "credible intervals support an interpretation of probability in terms of plausibility" [@morey:2015, p.120]. <!-- However, for Bayesian models so-called priors have to be chosen by researchers. -->

Before we move on to the next section, it is important to point out that **non-stochastic data is not an essential condition for applying the Bayesian approach**. The same approach is equally applicable to both non-stochastic and stochastic comparative datasets. Therefore, one can analyze both randomized comparative surveys (such as WJS) and comparative content analytic studies with the same Bayesian analytic approach.

## Bayesian analysis

What is the probability for this paper being accepted by *IJOC*? Under the frequentist framework (and if *IJOC* were accepting papers stochastically), we can only find this out by repeatedly submitting this paper to *IJOC*, say for 100 times, and then count the frequency of acceptance in these repeated submissions. It is indeed impractical as well as inhumane to the editorial team of *IJOC*. Instead, we assert before submission that this paper has a probability of 24% for being accepted. That is the published acceptance rate of a similar journal. After this paper is submitted and is not desk rejected, the probability might be around 24% to 30%. After a month of waiting and our confidence is shaken a little, the probability might decrease to 10% to 20%. After the paper is favorably reviewed by two reviewers and an R&R is invited, the probability might increase to 40% to 60%. If you see this paper on *IJOC*'s website, then the probability is beyond doubt 100% (or 0% if we submit this paper again).

@@

The $P(X| \theta)$ part is called likelihood function. In the *Journalism Studies* example, the likelihood function is based on rough rules from our experience and thus is not systematic. In actual analysis, we need to derive such a likelihood function based on the available data using methods such as Markov Chain Monte Carlo (MCMC). Nonetheless, the above equation indicates that there are only three ingredients in any Bayesian analysis: 1) data ($X$), 2) a method to derive the likelihood function $P(X | \theta)$ from the data, and 3) prior, $P(\theta)$.

We skip elaborating part 1, because some, but certainty not all, researchers have the means to amass a massive amount. The mechanism of how part 2 can be used to derive the likelihood function is beyond the scope of this paper. <!-- We provide a tutorial in Appendix I(+++TODO) for those who want to get an intuition. --> The current standard method, MCMC, is much more computationally intensive and has only been possible on desktop computers since the mid-1990s [@robert:2011:SHM]. And only in the last few years that can be done efficiently [@hoffman2014no], thanks to the probabilistic programming language *Stan* [@gelman:2015:S]. R interfaces to Stan, such as *brms* [@burkner2017advanced], make Bayesian analysis even more accessible to R users. But still, it is important to be mindful that Bayesian analysis is much more computational intensive than methods such as MLE. Our benchmark suggests that Bayesian analysis needs at least 100 times more running time than MLE.

Part 3 (Prior) is arguably the most controversial part of Bayesian analysis. In the *Journalism Studies* example, we can select a reasonable prior (or **informative** prior) of 24% from published information. Finding previous studies for an informative prior is the logical first thing to do. @keating:2019:W show that one in every seven communication research papers published in major communication journals was a form of replication attempt. For these one seventh of communication research, there should be previous studies available to base one’s informative prior non-controversially.

@@

But one person's expert opinion could be another person's wishful thinking. And this perceived subjectivity of specifying priors by experts’ judgment attracts wide-spread criticism from both statisticians [e.g. @efron1986isn] and social scientists [@elff:2020:MAF;@bryan:2015:MMC].

Undoubtedly, setting prior is consequential to the analysis [@van:2006:PB]. But the influence from priors is greatly weakened, when the data is getting bigger. Other than expert elicitation, another non-controversial way to specify priors --- at least in our opinion --- is to use  a weakly informative prior [@lemoine:2019:M]. In this way, one specifies only the possible range of the posterior<!-- [^4] -->. Some so-called "default weakly informative priors", e.g. $\mathcal{t}(1, 0, 0.25)$, have been suggested for typical regression models [@gelman:2008]. The documentation of Stan also provides information on how to choose an appropriate prior (https://github.com/stan-dev/stan/wiki/Prior-Choice-Recommendations).

@@

We used only the data from 2019 as the baseline. <!-- It is important to note that the Hong Kong protests, the 30th anniversary of the Tiananmen Square Protests and the 70th anniversary of the communist regime were in that year. Also, it was at the zenith of the US-China trade war.  -->

We excluded media outlets that contributed <1,000 articles in that year. This threshold allowed us to retain media outlets that the frequency of China coverage can be reliably estimated. In total, 61 media outlets from Spain (n = 11), Romania (n = 11), US (n = 7), Austria (n = 6), Germany (n = 5), Norway (n = 5), Australia (n  = 4), Brazil (n = 4), UK (n = 4), South Korea (n = 2), and the Netherlands (n = 2) were included. These 61 media outlets contributed 1,525,871 articles.

@@

In the article-level analysis, the data has 1,525,871 rows and each row represents an article. The data contains a binary dependent variable of China coverage ($y$), media outlet($j$), country of the outlet($k$), and distance measures ($x$).

@@

## Distance measures

>>>>

---
title             : "Bayesian multilevel modeling and its application in comparative communication research"
shorttitle        : "BAYESIAN MULTILEVEL REGRESSION"

@@

abstract: |
  Comparative approaches are frequently used in communication research, especially journalism studies. The purpose of this paper is to argue that Bayesian multilevel regression is a better option for analyzing comparative data. We argue that it is the only approach that can simultaneously account for non-atomicity (nested nature) and non-stochasticity (non-random sampling) of comparative data. Using the openly available *Worlds of Journalism Study* and *useNews* datasets and the R package *brms*, we demonstrate how to apply the Bayesian approach for the analysis of comparative data. We address the common challenges when using the Bayesian approach and highlight the advantages of posterior predictive checks for modeling checking.
keywords          : "Bayesian inference, multilevel model, comparative communication research, ecological effect"
wordcount         : "8964"

@@

```{r, echo = FALSE}
pts_tab <- readRDS("pts_tab.RDS")
require(brms)
import_brms <- readRDS("import_brms.RDS")
```

@@

Comparative approaches are frequently used in communication research, especially in journalism studies. Journalism studies are using the comparative approach [@hanusch:2019:C] to model journalistic culture [e.g. @esser:2013:C], news value [e.g. @burggraaff:2017:T;@wilke:2012], news flow [e.g. @wu:2000:SDI;@grasland:2019:I], among others. Around 40% of recent  comparative studies in journalism research are comparative content analysis [@hanusch:2019:C], which include news articles from various outlets and usually also from various countries. Then the included news articles are coded either manually or automatically. Another 10% of recent comparative studies in journalism research are surveys such as the Worlds of Journalism Study (WJS) [@hanusch:2017:CJC]. Although this article uses examples from journalism studies, the comparative approach is not bound to journalism studies and has been widely deployed in various subfields of communication. Comparative communication research is not exclusive to comparison across countries. Based on @de2017comparative’s classification, one can do comparisons across times, media, and other units [e.g. language regions within a multilingual country, see @vogler:2021:TNM]. In social media studies, for instance, it is common to compare content across sources [e.g. @zhao2019appealing]. The methodological issues discussed in this paper apply also to those cases.

Although some comparative studies are purely descriptive, most of these studies are aimed to study how contextual conditions such as characteristics of media outlets (e.g. political orientation, online versus offline) or their countries (e.g. post-communist country) influence the behaviors of journalists or the content of news articles . For example, some hypotheses are "the coverage of foreign countries by the news is primarily determined by geographical proximity and the status of the covered country" [@wilke:2012, p.306] and "the degree of opinion-orientation will be highest in newspapers from Polarized Mediterranean systems and lowest in those from Anglo-American systems." [@esser:2013:C] Employing the language from epidemiology [@susser:1994], the effect on media content and journalistic behaviors in these hypotheses is assumed to be ecological. It assumes a macro contextual factor (e.g., newspapers from Polarized Mediterranean systems) is associated with an outcome at the micro-level (e.g., degree of opinion-orientation), namely, the journalist-level or article-level.

This study of ecological effects on individual behaviors has a long tradition in social sciences. A famous example was Émile Durkheim's investigation on the ecological factors associated with suicide [@durkheim1897suicide]. Durkheim found a higher suicide rate among citizens from Scandinavian countries than those from other European countries. Using today’s standard, Durkheim's analysis is descriptive and this descriptive approach for studying ecological effect is indeed still useful for hypothesis generation in comparative research. An example of hypothesis-generating comparative research is <!-- redacted for ijoc  -->AUTHOR1 <!-- @chan2020combining -->, in which the sentiment profiles of terrorism coverage from Muslim- and Christian-majority countries were visualized. Hypothesis-generating comparative study, however, is rare. Most studies have a confirmatory outlook. As we see from the example hypotheses above, most of these studies propose hypotheses to test for ecological effects. In this context usually traditional (frequentist) hypothesis testing approaches were used: @esser:2013:C lumped multiple outlets from the same country together and then used univariate analysis of variance to test for the differences in the proportion of opinion-orienting articles across countries. In @wu:2000:SDI, multiple stepwise regression was used. These approaches violate the underlying assumptions. It highlights the fact that comparative research introduces a feature that researchers usually overlook: media contents are clustered in a multilevel structure. A news article is nested within its media outlet and its media outlet is in turn nested within its country. Such data structure brings two problems: non-atomicity and non-stochasticity. And specifically, we propose two solutions: multilevel modeling and Bayesian approach.

The goal of this paper is twofold. We use examples from journalism studies as the most critical cases in communication science to highlight the strength of multilevel models and the advantages of Bayesian models. In our paper, we first discuss these two issues before we suggest Bayesian multilevel regression as the best possible approach for comparative research in communication science and especially in journalism studies. Using the openly available WJS and *useNews* datasets and the R package *brms*, we then demonstrate how to apply a Bayesian approach for the analysis of comparative data.

## Multilevel models and non-atomicity

In comparative research, it is easy to incorrectly assume that macro-level independent variables (e.g. Anglo-American systems) could be analyzed at the same level as the micro-level dependent variable (e.g. the degree of opinion-orientation). The manifestation of this incorrect assumption is to enter macro-level variables as independent variables in multiple regression analysis and regress them against a micro-level dependent variable. Suppose one wants to study how the democratic performance of a country affects journalists’ perceived professional autonomy using the Worlds of Journalism data [Wave 1: @reich:2013:DJP; Wave 2: @hamada:2021:DJA]. The relationship can be expressed in the following regression equation: let $y_{i}$ be the dependent variable at the micro-level (journalist-level: perceived professional autonomy) and $x_{i}$ be the independent variable at the macro-level (country-level: democratic performance). Suppose there are $m$ journalists  where $i = 1,2,\ldots,m$.

@@

This method is the so-called "disaggregation approach". From an epistemic standpoint, searching for ecological effect by studying the value of slope ($\beta_{1}$) leads to the so-called atomistic fallacy [@hox2017multilevel]. From a statistical standpoint, this approach violates the underlying independence assumption. Almost all frequentist statistical tests assume that the observations are independent of each other: $y_{i}$ given $x_{i}$ are independently identically distributed (i.i.d.). Journalists from the same country are hardly i.i.d.: they are subjected to being governed by the same government and exposed to the same journalistic culture. Also, the way communication researchers survey the journalists resembles (nonrandom) cluster sampling rather than pure random sampling: one usually starts from a specific country and then surveys journalists from it. The choice of  countries is almost always not randomly selected. <!-- [^1] --> This sampling approach makes the independence assumption even more fragile.

@@

Previous simulation studies have shown that ignoring this dependence can lead to false-positive associations [e.g. @clarke:2008:W;@chen:2012:IIL]. The problem is more severe when the dependent variable is a discrete binary variable [@clarke:2008:W]. <!-- [^2] -->

@@

There are two solutions to this. The first solution is to aggregate the micro-level dependent variable across a macro-level independent variable. Suppose there are $n$ countries in the above example. One can aggregate the average level of $x$ as $z_{k}$ for the $k$-th country, where $k=i,\ldots,n$. Then, we can do a regression with a regression equation like so:

\begin{equation}
  \label{eq:2}
  z_{k} = \beta_{0} + \beta_{1} x_{k} + \epsilon_{k}
\end{equation}

Using this aggregation method, the unit of analysis effectively switches from journalist to country. This method is useful when $x$ is the only independent variable. It is not technically committing the atomistic fallacy, when one uses the value of slope as the evidence for an ecological effect. However, this method still has important drawbacks. First, it cannot be used for data with more than two levels. In those cases, the lower-level predictors were lumped together and in effect, assumed to be homogeneous and discarded. Second, this method discards a massive amount of information. It is better for analysis of a dependent micro-level variable with a reasonable aggregation function (e.g. counting a binary variable). For numerical variables, aggregation functions such as taking a mean or median cannot capture the spread of the micro-level variable [@bryk:1988:H]. Also, the effective sample size is reduced from the number of journalists ($m$) to the number of countries ($n$). Third, if one specifies hypotheses at the journalist-level but bases one’s conclusion on the aggregated analysis, this is a risk of interpreting the macro-level association wrongly at the micro-level, otherwise known as ecological fallacy. Nonetheless, this aggregation method, although inflexible, is still useful when the number of groups (e.g. $n$) is large. It is also useful to collapse micro-levels (e.g. article-level) that are not useful in answering one’s research questions.

Another solution is to use the multilevel model (linear mixed model, or hierarchical model). In a multilevel model, the effect on the micro-level dependent variable ($y$) is modeled with equations at different levels. Using the above example, $y_{ik}$ denotes the perceived professional autonomy of the $i$-th journalist in the $j$-th country; $x_{k}$ denotes the democratic performance of the $k$-th country.

@@

The benefit of using multilevel modeling lies in its flexibility in handling multi-level data. Suppose we also want to consider the clustering of journalists around $o$ different media organizations in the above example and $j$-th media media organization of the $i$-th journalist, where $j = 1,\ldots, o$ and if such data were available. [^WJSOUTLET] The multilevel regression equations are rewritten as:

@@

[^WJSOUTLET]: The data on media organizations are not available in the 2nd wave of the WJS dataset.

@@

Another way to look at the flexibility of multilevel modeling is the ability to vary other parameters in the regression equation as well. Suppose in another situation, a researcher is interested in analyzing the relationship between experience ($XP$) and perceived professional autonomy. Instead of assuming the effect to be uniform across countries, like in the following equation:

\begin{align}
y_{i} &= \beta_{0} + \beta_{1} XP_i + \epsilon_{i}
\end{align}

One can also assume the slope ($\beta_{1}$) to be a distribution that is governed by countries, i.e.

\begin{align}
y_{ik} &= \beta_{0} + \beta_{1} XP_{ik} + \epsilon_{ik} \\
\beta_{1} &= \gamma_{10} + \mu_{1k}
\end{align}

This model is called the varying slope model and is useful to establish robust estimation of effect (in this case $\gamma_{10}$) across all countries. In this paper, we will not go into detail of this kind of model. For an example of its application in comparative communication research, see @barnidge:2018:SMS.

In sum, multilevel modeling is the way to go for analyzing non-atomic data from comparative research. For surveys using probabilistic sampling, the conventional frequentist approach (maximum likelihood estimation, MLE) might still be valid and is available in most statistical packages [see an SPSS tutorial for communication researchers by @hayes:2006:PMM]. However, @stegmueller:2013:HMC demonstrates that MLE is associated with shrinkage (reduction of standard error, i.e. more false positives) and the shrinkage is more severe when the number of macro-level units (e.g. countries) is small. @stegmueller:2013:HMC proposes to use Bayesian analysis as a robust alternative [see counterarguments from @elff:2020:MAF]. Although less restrictive methods such as restricted maximum likelihood (REML) have been demonstrated to remediate the shrinkage issue of MLE [@elff:2020:MAF], we still agree with Stegmueller’s proposal for theoretical reasons. And for studies not using probabilistic sampling, we argue in the next section that the Bayesian approach is a better analytical approach.[@western:1994:BIC].

## Bayesian models and non-stochasticity

@@

Before diving into our theoretical reasoning, it is important to revisit what frequentist inference, the current default but often misunderstood [@rinke:2018:PMA] mode of inference in communication science, is. Under the frequentist framework, each experiment is assumed to be one of infinite independent, **repeatable** experiments on randomly drawn samples from a population. Random experiments are assumed to be repeated arbitrarily often. Based on this assumption and with just one experiment from the current study, we make an estimation about the population. The discrepancy between the estimation from that one experiment and the actual value of the population is due to sampling error alone, i.e. which subjects were randomly sampled from the population. Randomized surveys, for example, are assumed to be repeatable through repeated random sampling of the population. Suppose we replicated the same survey 100 times and we would obtain a slightly different sample every time. We then calculated the 90\% confidence interval of the mean for each of these 100 surveys. We should anticipate that roughly 90 out of these 100 confidence intervals would include the true mean of the population. We cannot say for sure exactly 90 out of these 100 confidence intervals would include the true mean of the population because repeated random sampling is indeed random and the process is **stochastic**. However, we can say 90 is more probable than 0 or 100.

Most of the comparative content analytic studies, unlike randomized surveys such as WJS, often collect all available content data from a bunch of selected media outlets. In contrast to cluster sampling where media outlets are sampled randomly from a sampling frame of all media outlets, these studies are collecting the entire population of observations from some nonprobailistically selected media outlets. In these census-like situations, there is no way to get more data unless the scope of these studies is changed [@berk:1995:SIA]. It is especially true for modern large-N studies using automated content analytic techniques. @burggraaff:2017:T, for instance, "collected **all** available news items from **a selection of major Dutch news outlets**, both online and print" (p. 6, emphasis added) and that amounted to 762,095 articles from 9 outlets in the period of 2014--2015. In that study, one could only get more data by including more media outlets or widening the time window. Unlike a repeatable survey like WJS, one can always randomly select more journalists from the sampling frame of all journalists in the respective country.

Therefore, these modern comparative content analytic studies are not repeatable and thus they generate non-stochastic data. It could be argued that data from these comparative content analytic studies are fundamentally irrelevant for frequentist inference [@western:1994:BIC]. Confidence intervals generated do not have the same meaning as those from repeatable studies. According to @western:1994:BIC [p. 413], these values from non-stochastic data "lack meaning even as abstract propositions". [^PVALUES]

[^PVALUES]: In this article, we will not go into detail of the null hypothesis statistical testing (NHST) and p-values, except in the Online Appendix. It is because for studies with a very large N, which comparative studies usually are, NHST is guaranteed to give positive results due to the so-called “Too Big To Fail” problem [see @lin:2013:RCT]. Also, researchers are usually not only interested in whether there is or isn’t an effect. Instead, we are interested in how large the magnitude and in what direction the effect is. Therefore, we will focus only on the point and interval estimations from various regression models.

A common counterargument to this is the classic one from @deming:1941:ICS [p. 45], who suggested that "[a]s a basis for scientific generalizations and decisions for action, a census is only a sample." This notion assumes a census of a population can be used to make inference on a theoretical device called *superpopulation* which "theoretically could exist, may have existed, or may exist in the future" [@gibbs:2015:IU, p.3]. In other words, a finite census-as-a-sample census is assumed to be a “representative sample” of an infinite superpopulation. This counterargument could be useful but unlike a regular random sample (cluster sample included), whose representativeness can be assessed, we can never assess the representativeness of the census-like data with respect to the theoretical superpopulation. Echoing the quote at the beginning of this paragraph, there is no way to tell if the current Czech history is representative of all possible Czech histories in the multiple parallel universes.

Instead of invoking the theoretical device of superpopulation, we follow the arguments from @western:1994:BIC and @stegmueller:2013:HMC for comparative studies: Bayesian inference should be used for analyzing data from comparative research in our field. Choosing a Bayesian approach also solves the problem of misinterpretation of confidence intervals [@rinke:2018:PMA]. Switching to a Bayesian approach addresses this issue as Bayesian "credible intervals support an interpretation of probability in terms of plausibility" [@morey:2015, p.120]. <!-- However, for Bayesian models so-called priors have to be chosen by researchers. -->

Before we move on to the next section, it is important to point out that **non-stochastic data is not an essential condition for applying the Bayesian approach**. The same approach is equally applicable to both non-stochastic and stochastic comparative datasets. Therefore, one can analyze both randomized comparative surveys (such as WJS) and comparative content analytic studies with the same Bayesian analytic approach. Besides these more abstract conceptual implications, choosing a Bayesian approach has some practical advantages, as we will later illustrate with the posterior predictive checks (PPCs), which can only be calculated if a Bayesian approach is used.

## Bayesian analysis as alternative

What is the probability for this paper being accepted by *IJOC*? Under the frequentist framework (and if *IJOC* were accepting papers stochastically), we can only find this out by repeatedly submitting this paper to *IJOC*, say for 100 times, and then count the frequency of acceptance in these repeated submissions. It is indeed impractical as well as inhumane to the editorial team of *IJOC*. Instead, we assert before submission that this paper has a probability of 24% for being accepted. That is the published acceptance rate of a similar journal. After this paper is submitted and is not desk rejected, the probability might be around 24% to 30%. After a month of waiting and our confidence is shaken a little, the probability might decrease to 10% to 20%. After the paper is mixed reviewed by three reviewers and an R&R is invited, the probability might increase to 40% to 60%. If you see this paper on *IJOC*'s website, then the probability is beyond doubt 100% (or 0% if we submit this paper again).

@@

The $P(X| \theta)$ part is called likelihood function. In the *IJOC* example, the likelihood function is based on rough rules from our experience and thus is not systematic. In actual analysis, we need to derive such a likelihood function based on the available data using methods such as Markov Chain Monte Carlo (MCMC). Nonetheless, the above equation indicates that there are only three ingredients in any Bayesian analysis: 1) data ($X$), which require no elaboration, 2) a method to derive the likelihood function $P(X | \theta)$ from the data, and 3) prior, $P(\theta)$.

R interfaces to Stan (the probabilistic programming language for conducting MCMC), such as *brms* [@burkner2017advanced], can enable the derivation of the likelihood function (Part 2). But still, it is important to be mindful that Bayesian analysis is much more computational intensive than methods such as MLE. Our benchmark suggests that Bayesian analysis needs at least 100 times more running time than MLE.

Part 3 (Prior) is arguably the most controversial part of Bayesian analysis. In the *IJOC* example, we can select a reasonable prior (or **informative** prior) of 24% from published information. Finding previous studies for an informative prior is the logical first thing to do. @keating:2019:W show that one in every seven communication research papers published in major communication journals was a form of replication attempt. For these one seventh of communication research, there should be previous studies available to base one’s informative prior non-controversially.

@@

But one person's expert opinion could be another person's wishful thinking. And this perceived subjectivity of specifying priors by experts’ judgment attracts wide-spread criticism from both statisticians [e.g. @efron1986isn] and social scientists [e.g. @elff:2020:MAF].

Undoubtedly, setting prior is consequential to the analysis. But the influence from priors is greatly weakened, when the data is getting bigger. Other than expert elicitation, another non-controversial way to specify priors --- at least in our opinion --- is to use a weakly informative prior [@lemoine:2019:M]. In this way, one specifies only the possible range of the posterior<!-- [^4] -->. Some so-called "default weakly informative priors", e.g. $\mathcal{t}(1, 0, 0.25)$, have been suggested for typical regression models [@gelman:2008].

@@

We used only the data from 2019 as the baseline<!-- . We --> and excluded media outlets that contributed <1,000 articles in that year. This threshold allowed us to retain media outlets that the frequency of China coverage can be reliably estimated. In total, <!-- 61 media outlets from Spain (n = 11), Romania (n = 11), US (n = 7), Austria (n = 6), Germany (n = 5), Norway (n = 5), Australia (n  = 4), Brazil (n = 4), UK (n = 4), South Korea (n = 2), and the Netherlands (n = 2) were included. These --> 61 media outlets contributed 1,525,871 articles.

@@

@@

## Distance measure: Trade volume
